Interactive Dashboard to Monitor the COVID-19 Outbreak and Vaccine Administration

### 2022-05-15 manuscript_covid19dashboard.Rmd
Updated

---
title: "Interactive Dashboard to Monitor the COVID-19 Outbreak and Vaccine Administration"
output: 
  pdf_document: 
    keep_tex: true
    number_sections: true
bibliography: references.bib
---

@@

Bar charts and line charts are the most frequently used tools for the visualization of total cases, daily cases, and weekly cases.
and comparisons with respect to time. Some dashboards contained doughnut-shaped pie charts to summarize
the total figures. In almost every dashboard, value boxes have been used to represent total figures.
Some dashboards contained interactive maps and data tables to visualize the distribution of cases by country,
province, region, or state. All dashboards are updated daily in real time. Gender, age groups, and ethnicity can be identified as common breakdowns. Most data sets and related links are available.

We used a colour-blind-friendly theme when creating our dashboard. The dashboard includes both static and interactive charts that can be used for explanation, exploration, and display. The data speaks to us, but it is not always easy to understand in what language they are doing it. Hence, we examine the same data under different angles using different types of plots. We do not have district-wise vaccination details. We do not have vaccination information per district. We'll save this for later. Our dashboard is completely replicable. The source code for reproducing the results is accessible in a public GitHub repository at https://github.com/thiyangt/covid19srilanka.

>>>>

---
title: "Interactive Dashboard to Monitor the COVID-19 Outbreak and Vaccine Administration"
header-includes:
   - \usepackage{url}
   - \usepackage{hyperref}
output: 
  pdf_document: 
    keep_tex: true
    number_sections: true
bibliography: references.bib
---

@@

Bar charts and line charts are the most frequently used tools for the visualization of total cases, daily cases, and weekly cases, and comparisons with respect to time. Some dashboards contained doughnut-shaped pie charts to summarize the total figures. In almost every dashboard, value boxes have been used to represent total figures.
Some dashboards contained interactive maps and data tables to visualize the distribution of cases by country, province, region, or state. All dashboards are updated daily in real time. Gender, age groups, and ethnicity can be identified as common breakdowns. Most data sets and related links are available.

We used a colour-blind-friendly theme when creating our dashboard. The dashboard includes both static and interactive charts that can be used for explanatory (telling you something), exploratory (give user the chance to interact with the plots), and exhibitory (showing data visually) purposes. The data speaks to us, but it is not always easy to understand in what language they are doing it. Hence, we examine the same data under different angles using different types of plots. We do not have district-wise vaccination details. This is a potential future direction to think about. Our dashboard is completely reproducible. The source code for reproducing the results is accessible in a public GitHub repository at https://github.com/thiyangt/covid19srilanka.

### 2022-05-15 manuscript_covid19dashboard.tex
Updated

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Interactive Dashboard to Monitor the COVID-19 Outbreak and Vaccine Administration},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=1in]{geometry}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
\ifluatex
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

@@

Bar charts and line charts are the most frequently used tools for the
visualization of total cases, daily cases, and weekly cases. and
comparisons with respect to time. Some dashboards contained
doughnut-shaped pie charts to summarize the total figures. In almost
every dashboard, value boxes have been used to represent total figures.
Some dashboards contained interactive maps and data tables to visualize
the distribution of cases by country, province, region, or state. All
dashboards are updated daily in real time. Gender, age groups, and
ethnicity can be identified as common breakdowns. Most data sets and
related links are available.

We used a colour-blind-friendly theme when creating our dashboard. The
dashboard includes both static and interactive charts that can be used
for explanation, exploration, and display. The data speaks to us, but it
is not always easy to understand in what language they are doing it.
Hence, we examine the same data under different angles using different
types of plots. We do not have district-wise vaccination details. We do
not have vaccination information per district. We'll save this for
later. Our dashboard is completely replicable. The source code for
reproducing the results is accessible in a public GitHub repository at
\url{https://github.com/thiyangt/covid19srilanka}.

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Interactive Dashboard to Monitor the COVID-19 Outbreak and Vaccine Administration},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=1in]{geometry}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
\usepackage{url}
\usepackage{hyperref}
\ifluatex
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

@@

Bar charts and line charts are the most frequently used tools for the
visualization of total cases, daily cases, and weekly cases, and
comparisons with respect to time. Some dashboards contained
doughnut-shaped pie charts to summarize the total figures. In almost
every dashboard, value boxes have been used to represent total figures.
Some dashboards contained interactive maps and data tables to visualize
the distribution of cases by country, province, region, or state. All
dashboards are updated daily in real time. Gender, age groups, and
ethnicity can be identified as common breakdowns. Most data sets and
related links are available.

We used a colour-blind-friendly theme when creating our dashboard. The
dashboard includes both static and interactive charts that can be used
for explanatory (telling you something), exploratory (give user the
chance to interact with the plots), and exhibitory (showing data
visually) purposes. The data speaks to us, but it is not always easy to
understand in what language they are doing it. Hence, we examine the
same data under different angles using different types of plots. We do
not have district-wise vaccination details. This is a potential future
direction to think about. Our dashboard is completely reproducible. The
source code for reproducing the results is accessible in a public GitHub
repository at \url{https://github.com/thiyangt/covid19srilanka}.
